Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
ARRRGGGHHH
Added AMDFusion citation.
Expanded results and conclusion.

@@

Based on the CPU-only and GPU-only runtimes of each benchmark, we were able to calculate an
optimal static data partitioning, such that the computations on the CPU and GPU took equal
time to complete.  Based on the disparity of runtimes between the CPU-only and GPU-only
results, the optimal runtimes ranged from a 2\% to nearly a 45\% speedup over just the GPU
alone.  Unfortunately,

@@

@@

\setboolean{@twocolumn}{false}
\newpage
\appendix[Team Member Contributions]
Kenneth Lee did A, B, C.  Kyle Morgan did X, Y, Z.
\end{document}

>>>>

With regard to the discrete GPU platform and the fused CPU+GPU platform, it
seems that the fused platform has some advantages.  For instance, consider 
Figures \ref{fig:reduction_discrete} and \ref{fig:reduction_fused}.  Although
we will not compare overall runtimes of the two benchmarks, we can see that
the GPU of the fused platform performed better than the GPU of the discrete
platform relative to their CPUs.  That is, the CPU outperformed the GPU on
the reduction benchmark on the discrete GPU architecture, but the converse
was true of the fused platform.  This may be due to the fact that the fused
platform shares memory between the CPU and GPU, which lowers data transfer
times between the two devices.  On the discrete GPU system, the GPU typically
experienced significant data transfer times for the GPU, and the effect of
this would be minimized on the fused platform.

@@

Based on the CPU-only and GPU-only runtimes of each benchmark, we were able to calculate an
optimal static data partitioning, such that the computations on the CPU and GPU took equal
time to complete.  Based on the disparity of runtimes between the CPU-only and GPU-only
results, the optimal runtimes ranged from a 2\% to nearly a 45\% speedup over just the GPU
alone.  Unfortunately, none of these theoretical results were supported in practice.  It seems
to be a limitation of OpenCL that it will not run kernels on different devices in parallel,
which effectively renders our load balancing schemes pointless.

Additionally, it seems that a fused CPU+GPU architecture may provide some performance benefits
over just a discrete GPU architecture.  Our results shows that the GPU outperformed the CPU on
the fused platform's reduction benchmark, but this was not the case for the discrete GPU platform.
However, as the CPUs and GPUs differed significantly between the two testing environments, we
cannot say definitively that one architecture will always be better than the other.

@@

\bibitem{AMDFusion}
http://fusion.amd.com

@@

\newpage
\appendix[Team Member Contributions]
Kenneth Lee did A, B, C.  Kyle Morgan did X, Y, Z.
\end{document}
